\textbf{ \Large {Decentralized autonomous sensor fault detection using neural networks}}

### 2015-02-18 Paper/PaperJahrSchlich.tex
Final corrections of the figures
summary

The neural network has been tested with varying numbers of training measurements (\autoref{fig:traininputs}).
With increasing numbers of training measurements, the prediction accuracy of the expected magnitude increases.

@@

This paper has shown a decentralized autonomous sensor fault detection strategy for structural health monitoring systems based on neural networks. 
Autonomous sensor fault detection has been realized by implementing a neural network into each sensor node.
The neural networks have been trained to predict expected sensor measurements to be compared to actual measurments, in order to detect sensor faults.
The SHM system has been verified with laboratory experiments, proving that sensor fault detection using neural networks can improve the dependability and the accuracy of structural health monitoring systems.

>>>>

The neural network has been tested with varying numbers of training measurements (\autoref{fig:traininputs}).
With increasing numbers of training measurements, the prediction accuracy of the expected magnitude increases.
With 24 training measurements, a minimum deviation---between the expected magnitude and the measured magnitude---of average 0.47\% has been reached.

@@

This paper has shown a decentralized autonomous sensor fault detection strategy for structural health monitoring systems based on neural networks. 
Autonomous sensor fault detection has been realized by implementing a neural network into each sensor node.
The neural networks have been trained to predict expected sensor measurements to be compared to actual measurments, in order to detect sensor faults.
The structural integrity of the monitored structure are detected by observing the natural frequency.
To verify the proposed approach, the SHM system has been installed on a test structure to be tested in laboratory experiments.
During several testruns, the prediction accuracy could be reduced up to a deviation of average 0.47\%.
Simulated sensor faults have been detected reliably.
Through decentralized data processing, embedded in each sensor node, the data traffic has been reduced by 99.3\,\%.
It has been proven, that sensor fault detection using neural networks can improve the dependability and the accuracy of structural health monitoring systems.
